---
title: "Relationship between a set of variables and MPG"
author: "Dongjun_Cho"
date: "7/7/2020"
output:
  html_document: default
  pdf_document: default
---

## Summary

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* Is an automatic or manual transmission better for MPG
* Quantify the MPG difference between automatic and manual transmissions

## Analysis

Brief analysis of dataset
```{r}
data <- mtcars
head(data)
dim(data)
summary(data)
```


Multivariable Regression / Interpretation
```{r}
summary(lm(mpg ~. -1, data))$coef
```

Data Format

-	mpg 	: Miles/(US) gallon
- cyl 	: Number of cylinders
- disp 	: Displacement (cu.in.)
- hp 	  : Gross horsepower
- drat 	: Rear axle ratio
- wt 	  : Weight (1000 lbs)
- qsec 	: 1/4 mile time
- vs 	  : Engine (0 = V-shaped, 1 = straight)
- am 	  : Transmission (0 = automatic, 1 = manual)
- gear 	: Number of forward gears
- carb 	: Number of carburetors 


```{r}
pairs(data, panel=panel.smooth, main ="Car")

```


MPG by type of transmission

Automatic
```{r}
summary(data[data$am == 0, "mpg"])
```


Manual
```{r}
summary(data[data$am == 1, "mpg"])
```


Plot into ggplot 
```{r}
library(ggplot2)
ggplot(data, aes(x= factor(am, level=c(0,1), labels= c("Automatic","Manual")), y=mpg)) + geom_boxplot()+ labs(title ="MPG by type of transmission", x= "Transmission Type", y="Mpg (Miles/(US) gallon)")

```

Multiple variable in models

Using step function to see variable impact by adding other variable
```{r}
par(mfrow =c(2,2))
fit <- step(lm(mpg ~ ., data))
summary(fit)
plot(fit)
```


## Conclusions

Through analyzing the mtcars dataset, we found that manual transmission cars have more mpg (miles per gallon) than automatic transmission cars.

We also found that wt/qsec/am predictor is the best model. Multiple R-squared values for this model are 84.97% which is high enough for mpg outcome.
